### 2025-09-18 paper/sec/introduction.tex
Supporting citations for intro.

Making sense of and verifying data-driven claims is hard, even when the evidence base (data sets and related
analyses) is open. We see this in peer review, misinformation, retracted papers, \rpnote{supporting
citations}. The ability of LLMs to assist with these challenges has received considerable attention recently,
for example in quantity extraction~\citep{bolucu23}, scientific fact-checking~\citep{abu-ahmad25}, and
scientific figure interpretation~\citep{roberts24}.

@@

\begin{figure}%[h]
    \centering
    \includegraphics[width=\linewidth]{fig/scigen-1805.02474v1-10-with-pointer.png}
    \vspace{1mm}
    \hrule
    \includegraphics[width=\linewidth]{fig/scigen-1805.02474v1-10-counterfactual-with-pointer.png}
    \caption{\emph{Transparent document} example, showing counterfactual behaviour}\label{fig:scigen-example-website}
\end{figure}

>>>>

Making sense of and verifying data-driven claims is hard, even when the evidence base (data sets and related
analyses) is in the public domain. Expert reviewers often struggle to evaluate empirical
claims~\citep{weber20}; paper retractions are frequently attributable to (non-fraudulent but significant)
errors in data management and analysis~\citep{hu25}. The ability of LLMs to assist with these challenges has
received considerable attention recently, for example in scientific fact-checking~\citep{abu-ahmad25} and
figure interpretation~\citep{roberts24}.

@@

\begin{figure}%[h]
    \centering
    \includegraphics[width=\linewidth]{fig/scigen-1805.02474v1-10-with-pointer.png}
    \vspace{1mm}
    \hrule
    \includegraphics[width=\linewidth]{fig/scigen-1805.02474v1-10-counterfactual-with-pointer.png}
    \caption{\emph{Transparent document} example (top); counterfactual behaviour (bottom)}\label{fig:scigen-example-website}
\end{figure}
